The Emergent Simplicity of Galaxy Size

### 2017-09-29 paper/galsize_paper.tex
Updated results section

In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the model described in \S\ref{sec:model}.

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the model described in \S\ref{sec:model}. Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since the model parameters were taken directly from \citet{kravtsov13}, which were fit to the one-point measurements in Fig.~\ref{fig:scatter_plot}, whereas the two-point measurements appearing in Figure \ref{fig:clustering_ratio_upshot} have heretofore never been measured.

@@

The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result. This feature also holds true for model galaxies. This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here. We present a resolution to this puzzle in the following section.

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
\caption{
{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies. The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos"). In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
}
\label{fig:shuffle}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the K13 model described in \S\ref{sec:model}.

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.

@@

The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result. This feature also holds true for model galaxies. This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.

A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}.

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
\caption{
{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies. The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos"). In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
}
\label{fig:censatsizehist}
\end{figure}
%-----------------------------------------------------------------------------------------------------
